Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-03 Arxiv/main.tex
update privacy proof
Update main.tex

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{4} \big) \\
  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{4} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

@@

After post-processing (i.e., taking the floor value of $Y$), we get:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
When $\alpha = \beta$, we also have:
\begin{align*}
 Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
  = \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
 \end{align*}
 By simplifying the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:
\begin{itemize}
  \item[\textbf{case 1:}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

  We also have:
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
  \end{align*} 
  when $\alpha = \beta$.

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
  \qquad &
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

  we also have: 
  \begin{align*}
   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  \geq \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
  \end{align*}
  when $\alpha = \beta$

\end{itemize}

>>>>

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  \exp
  \big(
  \frac{\epsilon}{4} \cdot \gamma
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \unomalizer{\dataobs'}
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

@@

After post-processing (i.e., taking the floor value of $Y$), we get:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t \geq 0$, and\\
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t < 0$.\\

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$. By applying Hellinger distance in our case, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
when $t \geq 0$, and\\
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\end{array}
$$
when $t < 0$.\\

% When $\alpha = \beta$, we also have:
% \begin{align*}
%  Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
% \leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
%   = \quad & Pr[ - t \leq Y < t + 1] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
%  \end{align*}
Unfolding the Hellinger distance formula($\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$), we get:
\begin{itemize}
  \item[\textbf{case}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

%   We also have:
%   \begin{align*}
%   & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
%   \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
%   \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
%   \cdot
%   \prod_{k = 1}^{\frac{t}{2}}
%   \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
%   = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}}),
%   \end{align*} 
%   when $\alpha = \beta$.
% in 2 dimensions, where $\epsilon = 1.0$. 
% \begin{itemize}
% 	\item \textbf{Case} of baseline Laplace mechanism, where $\Delta \bysinfer = 2$:\\

% 	\item \textbf{Case} of improved Laplace mechanism, where $\Delta \bysinfer = 1$
% \end{itemize}

  \item[\textbf{case}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
  \qquad &
  1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
\frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}\\
\qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}
  % we also have: 
  % \begin{align*}
  %  Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  % \qquad &
  % 1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  % \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  % \qquad &\cdot 
  % \prod_{k = 0}^{m-1}
  % \sqrt{(1 + \frac{1}{2(\alpha + k)})
  % (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  % } \\
  % \qquad & \cdot 
  % \prod_{k = 1}^{m} 
  % \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  % \geq \quad & Pr[ - t \leq Y < t + 1] \\
  % = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})
  % \end{align*}
  % when $\alpha = \beta$
\end{itemize}

In both cases, $Pr[\hellinger(\bysinfer(\dataobs), r_L )^2 = 0]$ asymptotically equal to 1 when data size increases.
